---
title: "Lab 08 - University of Edinburgh Art Collection"
author: "Lilly McClendon"
date: "03.28.2025"
output: github_document
---

## Load Packages and Data  

```{r load-packages, message = FALSE}
library(tidyverse) 
library(rvest)
```

```{r load-data, message = FALSE, eval = TRUE}
# Remove eval = FALSE or set it to TRUE once data is ready to be loaded
uoe_art <- read_csv("data/uoe-art.csv")
```

## Exercise 9

Let's start working with the **title** column by separating the title and the date:  

```{r separate-title-date, error = TRUE}
uoe_art <- uoe_art %>%
  separate(title, into = c("title", "date"), sep = "\\(") %>%
  mutate(year = str_remove(date, "\\)") %>% as.numeric()) %>%
  select(title, artist, year, date)
```


## Exercise 10  

The warnings mean that there are parts that are not numeric like unknown or possibly. We're okay with leaving the warnings in because our aim is to capture the year when it is convenient to do so, and if it says unknown or has extraneous information that is not a number we don't care because we are looking for the year which is numeric data. 

Feel free to add code chunks as needed. Don't forget to label your code chunk.


## Exercise 11  

```{r skim}
library(skimr)
skim(uoe_art)
```

111 pieces have artist information missing and 1575 pieces have year information missing. 

## Exercise 12

```{r histogram}
library(ggplot2)
ggplot(uoe_art, aes(x = year)) + 
  geom_histogram(bins = 50)
```

There is a value out of the ordinary which is very close to 0 while the next earliest piece made is in the 19th century.  

## Exercise 13

```{r manual_adjust_DeathMask_Piece}
# Piece Death Mask in row 1413 has the title Death Mask (2) (1964) and the code above was using (2) for the year and date. The code below manually changes it to be correct.

library(dplyr)
uoe_art_corrected <- uoe_art %>% 
  mutate(year = if_else(row_number() == 1413, 1964, year))

min(uoe_art_corrected$year, na.rm = TRUE)
max(uoe_art_corrected$year, na.rm = TRUE)
```

```{r histogram_with_corrected_data}
library(ggplot2)
ggplot(uoe_art_corrected, aes(x = year)) + 
  geom_histogram(bins = 25)
```


Our code did not originally capture the correct year information because it was looking at the first parentheses and this piece had two sets of parentheses in the title. 

## Exercise 14 

```{r most_featured_artist}
library(dplyr)
uoe_art_corrected %>% 
  count(artist)%>%
  arrange(desc(n))
```

The most commonly featured artist in the collection is Emma Gillies. I have never heard of Emma Gillies before, but it seems logical the most pieces in the collection would be from her as she studied at the Edinburgh College of Art. Her brother (also an artist) had served as the Director of the Edinburgh College of Arts. As Emma Gillies passed away at a young age, it seems that her brother may have donated her pieces so that they could be viewed and her work recognized. 


## Exercise 15

```{r child_in_title}
library(stringr)
library(dplyr)

filtered_uoe_art_corrected <- uoe_art_corrected %>% 
  filter(rowAny(
    across(
      .cols = c(title), 
      .fns = ~str_detect(., regex("child", ignore_case = TRUE))
  )))
```

____ Pieces have the word child in the title. 

