---
title: "Lab 08 - University of Edinburgh Art Collection"
author: "Lilly McClendon"
date: "03.28.2025"
output: github_document
---

## Load Packages and Data  

```{r load-packages, message = FALSE}
library(tidyverse) 
library(rvest)
```

```{r load-data, message = FALSE, eval = TRUE}
# Remove eval = FALSE or set it to TRUE once data is ready to be loaded
uoe_art <- read_csv("data/uoe-art.csv")
```

## Exercise 9

Let's start working with the **title** column by separating the title and the date:  

```{r separate-title-date, error = TRUE}
uoe_art <- uoe_art %>%
  separate(title, into = c("title", "date"), sep = "\\(") %>%
  mutate(year = str_remove(date, "\\)") %>% as.numeric()) %>%
  select(title, artist, year, date)  
```


## Exercise 10  

The warnings mean that there are parts that are not numeric like unknown or possibly. We're okay with leaving the warnings in because our aim is to capture the year when it is convenient to do so, and if it says unknown or has extraneous information that is not a number we don't care because we are looking for the year which is numeric data. 

Feel free to add code chunks as needed. Don't forget to label your code chunk.


## Exercise 11  

```{r skim}
library(skimr)
skim(uoe_art)
```

111 pieces have artist information missing and 1575 pieces have year information missing. 

*Continue with the same structure as above.*

You're doing great—keep going! Follow the same format and add your response below.  


## Additional Exercises  

Almost there! Keep building on your work and follow the same structure for any remaining exercises. Each exercise builds on the last, so take your time and make sure your code is working as expected.  
